Bow shocks, bow waves, and dust waves. II. Beyond the rip point

### 2019-03-18 papers/Papers1234/sec-dust-wave-discussion.tex
Finish Jane corrections to Paper II

In the inertia-confined case, the radius \(R\starstar\) is
proportional to the single-grain opacity \(\kappa\grain\) and will
therefore vary with grain size and composition.  For a spherical grain
of radius \(\amu\,\si{\um}\) and solid density
\(\rho\grain \, \si{g.cm^{-3}}\), equation~\eqref{eq:kappa-grain} yields
\begin{equation}
  \label{eq:kappa-d-dependence}
  \kappa\grain = 7500 \frac{\Qpbar}{\rho\grain \amu} \ . 
\end{equation}
The radiation pressure efficiency is \(\Qpbar \sim 1\) for
\(\amu > 0.02\), but falls as \(\Qpbar \propto a\) for smaller grains
\citep[e.g., Fig.~7 of][]{Draine:2011a}.  Therefore, all the smallest
grains will form the dust wave at the same point, but grains larger
than \SI{0.02}{\um} will be spread out with
\(R\starstar \propto a^{-1}\).  It might be thought that this would produce
a very broad diffuse appearance to the dust wave, but this is
mitigated by the fact that it is the smaller grains that dominate the
UV opacity and mid-IR emissivity.  Also, the larger grains may be
destroyed by radiative torques (see \S~\ref{sec:grain-survival-dust}).
For the drag-confined case, the situation is clearer since the dust
wave will form just inside the rip point, \(R_\dag\), which is relatively
insensitive to the grain size.

@@

The survival of dust grains of different sizes in close proximity to
OB stars is something that must be considered.  Potential destruction
mechanisms include thermal evaporation, particle sputtering, and
radiative torque destruction.  Thermal evaporation requires that the
grain radiative equilibrium temperature exceed the sublimation
temperature (\SIrange{1500}{2000}{K}, depending on composition), which
occurs for radiative fluxes about \SI{e9} times higher than the
interstellar radiation field.  For a drag-confined dust wave, we have
a fixed radiation parameter \(\Xi_\dag \sim 1000\), so this becomes a
threshold on the gas density, requiring \(n > \SI{3e5}{cm^{-3}}\).
Combining this with the maximum allowed density for a dust wave
(eq.~[\ref{eq:dust-wave-high-density-condition}]), we also obtain a
condition on the stream velocity:
\(v_\infty > 170 \kappa_{600}^{0.5} L_4^{0.15} \, \si{km.s^{-1}}\).  Therefore,
thermal evaporation is generally unimportant in dust waves, except for
fast-moving stars in very high density environments.

@@

Radiative torque disruption \citep{Hoang:2018a} is the centrifugal
rupture of an irregular grain of non-zero helicity that has been
suprathermally spun up by the anisotropic absorption of radiation
\citep{Dolginov:1976a, Draine:1996b, Lazarian:2007a}.  The process has
a very steep size dependence, being most effective in destroying
larger grains.  Using \citeauthor{Hoang:2018a}'s equation~(27) and
assuming a grain tensile strength of
\(S_{\text{max}} = \SI{2e10}{dyne.cm^{-2}}\) \citetext{\S~2.4 of
  \citealp{Borkowski:1995a}}, we find that grains larger than
\(\amu \sim 0.04\, n^{-0.123}\) are efficiently destroyed by this
mechanism at a distance \(R_\dag\) from the star. The spin-up timescales
are less than \(100\, n^{-1}\,\si{yr}\), which is short compared with
the dust wave dynamic timescale.

>>>>

In the inertia-confined case, the radius \(R\starstar\) is
proportional to the single-grain opacity \(\kappa\grain\) and will
therefore vary with grain size and composition.  For a spherical grain
of size \(\amu\,\si{\um}\) and solid density
\(\rho\grain \, \si{g.cm^{-3}}\), equation~\eqref{eq:kappa-grain} yields
\begin{equation}
  \label{eq:kappa-d-dependence}
  \kappa\grain = 7500 \frac{\Qpbar}{\rho\grain \amu} \ . 
\end{equation}
The radiation pressure efficiency is \(\Qpbar \sim 1\) for
\(\amu > 0.02\), but falls as \(\Qpbar \propto a\) for smaller grains
\citep[e.g., Fig.~7 of][]{Draine:2011a}.  Therefore, all the smallest
grains will form the dust wave at the same point, but grains larger
than \SI{0.02}{\um} will be spread out with
\(R\starstar \propto a^{-1}\).  It might be thought that this would produce
a very broad diffuse appearance to the dust wave, but this is
mitigated by the fact that it is the smaller grains that dominate the
UV opacity and mid-IR emissivity.  Also, the larger grains may be
destroyed by radiative torques (see \S~\ref{sec:grain-survival-dust}).
For the drag-confined case, the situation is clearer since the dust
wave will form just inside the rip point, \(R_\dag\), which is relatively
insensitive to the grain size.

@@

The survival of dust grains of different sizes in close proximity to
OB stars is something that must be considered.  Potential destruction
mechanisms include thermal evaporation, particle sputtering, and
radiative torque destruction.  Thermal evaporation requires that the
grain radiative equilibrium temperature exceed the sublimation
temperature (\SIrange{1400}{1750}{K}, depending on composition), which
occurs for radiative fluxes about \SI{e9} times higher than the
interstellar radiation field.  For a drag-confined dust wave, we have
a fixed radiation parameter \(\Xi_\dag \sim 1000\), so this becomes a
threshold on the gas density, requiring \(n > \SI{3e5}{cm^{-3}}\).
Combining this with the maximum allowed density for a dust wave
(eq.~[\ref{eq:dust-wave-high-density-condition}]), we also obtain a
condition on the stream velocity:
\(v_\infty > 170 \kappa_{600}^{0.5} L_4^{0.15} \, \si{km.s^{-1}}\).  Therefore,
thermal evaporation is generally unimportant in dust waves, except for
fast-moving stars in very high density environments.

@@

Radiative torque disruption \citep{Hoang:2018a} is the centrifugal
rupture of an irregular grain of non-zero helicity that has been
suprathermally spun up by the anisotropic absorption of radiation
\citep{Dolginov:1976a, Draine:1996b, Lazarian:2007a}.  The process has
a very steep size dependence, being most effective in destroying
larger grains.  Using equation~(27) of \citet{Hoang:2018a} and
assuming a grain tensile strength of
\(S_{\text{max}} = \SI{2e10}{dyne.cm^{-2}}\) \citetext{\S~2.4 of
  \citealp{Borkowski:1995a}}, we find that grains larger than
\(\amu \sim 0.04\, n^{-0.123}\) are efficiently destroyed by this
mechanism at a distance \(R_\dag\) from the star. The spin-up timescales
are less than \(100\, n^{-1}\,\si{yr}\), which is short compared with
the dust wave dynamic timescale.

### 2019-03-18 papers/Papers1234/sec-weak-coupling.tex
Finish Jane corrections to Paper II

Example results are shown in the bottom row of
Figure~\ref{fig:multi-dustprops} and again they are qualitatively
similar for all the simulations.  Close to the star, the radiation
force is higher than the upper limit on the Coulomb drag force
(eq.~\eqref{eq:fdrag-maximum}), so that the equilibrium drift velocity
is exceedingly high.  We discuss this situation in greater detail
below in \S~\ref{sec:drag-force-grains}.  Note that such high drift
velocities are much higher than any realistic true relative velocity
between grains and gas, since they are based on the assumption that
the radiation force remains constant while the grain is accelerated,
which is not the case under these conditions.  Instead, they are
simply an indication that the gas and grains have completely
decoupled.

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/existence-dust-wave}
  \caption{Regions of stream parameter space \((v, n)\) where dust
    waves may form around main-sequence OB stars of
    \SIlist{10;20;40}{M_\odot} with standard wind parameters (see
    Tab.~\ref{tab:stars}).  This figure is similar to Paper~I's
    Fig.~2, except that the velocity axis is logarithmic and extends
    out to \SI{1000}{km.s^{-1}}.  Overlapping colored shapes show
    parameters where dust waves may be allowed in the cases of large
    (\(a = \SI{0.2}{\um}\)) and small (\(a = \SI{0.02}{\um}\))
    graphite and silicate grains, as labeled in the left panel.  For
    \((v_\infty, n)\) outside of these shapes, dust waves cannot occur for
    the reasons indicated by labeled orange arrows in the center
    panel.  Labeled dashed lines in the right panel show the
    correspondence between the region boundaries and each dust wave
    existence condition given in
    equations~(\ref{eq:dust-wave-velocity-condition},
    \ref{eq:dust-wave-low-density-condition},
    \ref{eq:dust-wave-high-density-condition}). Heavy dashed lines in
    the left panel show where the rip point and the drag-free
    turnaround radius coincide.  Dust waves above and to the left of
    these lines are drag confined, while dust waves below and to the
    right of the lines are inertia confined.  }
  \label{fig:existence-dust-wave}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/dust-wave-phase-trajectories-annotate}
  \caption{Trajectories of small graphite grains
    (\(a = \SI{0.02}{\um}\)) at impact parameter \(b = 0\) for two
    example cases (see yellow ``+'' symbols in left panel of
    Fig.~\ref{fig:existence-dust-wave}), which differ only in the
    stream velocity: \(v = \SI{40}{km.s^{-1}}\) (left panels) and
    \SI{80}{km.s^{-1}} (right panels).  In both cases, the stream
    density is \(n = \SI{1}{cm^{-3}}\) and the central star is a
    \SI{10}{M_\odot} main-sequence B star (see Tab.~\ref{tab:stars}).
    Upper panels show the evolution of grain radius, \(R\) (blue
    curve, normalized by the rip point radius, \(R_\dag\)), and grain
    velocity, \(v\) (orange curve, normalized by the gas stream
    velocity).  The origin of the time axis is set to the moment of
    closest approach of the grain to the star: \(R = \Rmin\).  Lower
    panels show the trajectories in phase space: position versus
    gas--grain relative slip velocity (\(w = \abs{v - v_\infty}\)).  Filled
    contours show the net force on the grain: \(f\rad - f\drag\), with
    positive values in blue and negative values in red.  The heavy
    dotted line shows where there is no net force: \(f\rad = f\drag\).
    The grain trajectory (thick, solid black line with arrows)
    initially follows this line, but departs from it after the rip
    point. In the left panel, the grain enters a limit cycle between
    decoupling (rip) and re-coupling (snap back).  In the right panel,
    the grain spirals in on the stagnant drift point.  See text for
    further details.}
    \label{fig:phase-space-trajectories}
\end{figure*}

@@

An example of each of these two behaviors is illustrated in
Figure~\ref{fig:phase-space-trajectories}.  The left panels show the
case where \(v_\infty = \SI{40}{km.s^{-1}}\), which is in the unstable
regime, resulting in periodic ``limit-cycle'' behavior (the parameters
of this model correspond to the yellow ``plus'' symbol labeled ``40''
in the left panel of Fig.~\ref{fig:existence-dust-wave}).  During the
grain's first approach, it starts to follow a phase trajectory (lower
left panel) along the \(f\rad - f\drag = 0\) contour, corresponding to
equilibrium drift, in which the grain begins to move a few
\si{km.s^{-1}} slower than the gas stream.  Then, when it reaches the
rip point (\(R = R_\dag\), \(w \approx \SI{10}{km.s^{-1}}\)) it suddenly
experiences a large unbalanced outward radiation force (blue region of
phase space in Fig.~\ref{fig:phase-space-trajectories}). The grain's
inward momentum carries it to the point \(\Rmin \approx 0.85 R_\dag\), before
it is expelled at roughly twice the inflow speed.  However, after
moving outward, it finds itself in a drag-dominated region of phase
space (red in the figure), and so recouples to the inflowing gas
stream.  The recoupling initiates gradually, as the grain's outward
motion is slowed and it begins to move inward again, but is completed
suddenly once \(w\) again falls below \SI{10}{km.s^{-1}}, in what we
term \textit{snap back}. The net result is that the grain has returned
to exactly the same phase track that it started in on, and so repeats
the cycle indefinitely.

@@

If \(r\B / \Rmin \ll 1\), then the grains are so strongly coupled to the
field that they can be treated in the guiding-center approximation, in
which the trajectory is decomposed into a tight circular gyromotion
around the field lines, plus a sliding of the guiding center along the
field lines, which is governed by the radiation and drag forces.  The
radiation force will also produce an out-of-plane drift, given by
\begin{equation}
  \label{eq:perpendicular-drift}
  \bm{v}_{\text{drift}} = \frac{c}{e z\grain} \, \frac{\bm{f}\!\rad \times \bm{B}}{B^2}
  \ ,
\end{equation}
but from equations~(\ref{eq:Larmor}, \ref{eq:dust-rad-force},
\ref{eq:dust-r0}) it follows that
\begin{equation}
  \label{eq:vdrift-over-vinfinity}
  \frac{v_{\text{drift}}(R\starstar)}{v_\infty} = \frac{r\B}{2 R\starstar} \ ,
\end{equation}
so it is valid to ignore this drift in the limit of small \(r\B\).
This is the limit that was applied in \S~\ref{sec:tight-magn-coupl}
for the case of zero drag.  In the opposite limit,
\(r\B / \Rmin \gg 1\), magnetic coupling is so weak that the
non-magnetic results of \S~\ref{sec:imperf-coupl-betw} are scarcely
modified.  Assuming \(w_\perp \sim v_\infty\) and adopting a threshold of
\(r\B / \Rmin < 0.1\), equations~(\ref{eq:larmor-over-Rdag},
\ref{eq:larmor-over-Rstarstar}) can be transformed into conditions on
the stream velocity (in \si{km.s^{-1}}) where tight magnetic coupling
will apply: \newcommand\freeze{\ensuremath{_{\text{tight}}}}
\begin{equation}
  \label{eq:velocity-strong-B-coupling}
  v_{\infty} < v\freeze \approx
  \begin{cases}
    \text{drag-confined:}
    & 0.8 \, a_{\si{\um}}^{-2} \, v\alfven \, L_4^{1/2}\\
    \text{inertia-confined:}
    & 6 \, a_{\si{\um}}^{-1} \, v\alfven^{1/3} \, n^{1/6} \, L_4^{1/3} \\
  \end{cases} \ ,
\end{equation}
where we have substituted typical values of the minor parameters
\(\Xi_\dag\), \(\phi_{\dag}\), \(\phi_{**}\), \(\rho\grain\),
\(T_4\).\footnote{%
  The most significant systematic variation in \(v\freeze\) from these
  suppressed parameters is due to grain composition, yielding slightly
  higher values for graphite than for silicate (\SI{+-0.15}{dex}).} %
It is apparent that \(v\freeze\) is very sensitive to the grain size.
For instance, taking a typical \hii{} region value of
\(v\alfven = \SI{2}{km.s^{-1}}\) \citep{Arthur:2011a} and
\(L_4 = 0.63\) (Tab.~\ref{tab:stars}, B1.5~V star), then for the
drag-confined case \(v\freeze \approx \SI{30}{km.s^{-1}}\) for \SI{0.2}{\um}
grains but \(v\freeze \approx \SI{3000}{km.s^{-1}}\) for \SI{0.02}{\um}
grains. Thus, for typical stream velocities of
\SIrange{20}{100}{km.s^{-1}}, the small grains are always tightly
coupled to the magnetic field, but the large grains are only loosely
coupled for the faster streams.

@@

In panel~b, corresponding to \(v_\infty = \SI{80}{km.s^{-1}}\), the grain
settles for a while around the stagnant drift radius, \(R_\ddag\), after
the initial rip and turn around.  Again, it slowly migrates sideways,
and eventually recouples to the incident stream, but this time after
reaching \(y \approx +R_\ddag\).  The grain residence time in the apex region,
measured in crossing times, is slightly longer than in panel~a, but is
of the same order.  In both these cases, a second, exterior dust
shell is formed in addition to the hemispherical one produced by the
initial turn around inside \(R_\dag\). In the limit-cycle case, it forms
at the snap-back point, while in the stagnant-drift case, it forms at
\(R_\ddag\) and is significantly denser than the interior shell (upper
right panel of Fig.~\ref{fig:frozen-stream}).

>>>>

Example results are shown in the bottom row of
Figure~\ref{fig:multi-dustprops} and again they are qualitatively
similar for all the simulations.  Close to the star, the radiation
force is higher than the upper limit on the Coulomb drag force
(eq.~[\ref{eq:fdrag-maximum}]), so that the equilibrium drift velocity
is exceedingly high.  We discuss this situation in greater detail
below in \S~\ref{sec:drag-force-grains}.  Note that such high drift
velocities are much higher than any realistic true relative velocity
between grains and gas, since they are based on the assumption that
the radiation force remains constant while the grain is accelerated,
which is not the case under these conditions.  Instead, they are
simply an indication that the gas and grains have completely
decoupled.

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/existence-dust-wave}
  \caption{Regions of stream parameter space \((v, n)\) where dust
    waves may form around main-sequence OB stars of
    \SIlist{10;20;40}{M_\odot} with standard wind parameters (see
    Tab.~\ref{tab:stars}).  This figure is similar to Paper~I's
    Fig.~2, except that the velocity axis is logarithmic and extends
    out to \SI{1000}{km.s^{-1}}.  Overlapping colored shapes show
    parameters where dust waves may be allowed in the cases of large
    (\(a = \SI{0.2}{\um}\)) and small (\(a = \SI{0.02}{\um}\))
    graphite and silicate grains, as labeled in the left panel.  For
    \((v_\infty, n)\) outside of these shapes, dust waves cannot occur for
    the reasons indicated by labeled orange arrows in the center
    panel.  Labeled dashed lines in the right panel show the
    correspondence between the region boundaries and each dust wave
    existence condition given in
    equations~(\ref{eq:dust-wave-velocity-condition},
    \ref{eq:dust-wave-low-density-condition},
    \ref{eq:dust-wave-high-density-condition}). Heavy dashed lines in
    the left panel show where the rip point and the drag-free
    turnaround radius coincide.  Dust waves above and to the left of
    these lines are drag confined, while dust waves below and to the
    right of the lines are inertia confined.  Yellow plus symbols show
    the parameters for the two example trajectories shown in
    Fig.~\ref{fig:phase-space-trajectories}.}
  \label{fig:existence-dust-wave}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/dust-wave-phase-trajectories-annotate}
  \caption{Trajectories of small graphite grains
    (\(a = \SI{0.02}{\um}\)) at impact parameter \(b = 0\) for two
    example cases (see yellow ``+'' symbols in left panel of
    Fig.~\ref{fig:existence-dust-wave}), which differ only in the
    stream velocity: \(v = \SI{40}{km.s^{-1}}\) (left panels) and
    \SI{80}{km.s^{-1}} (right panels).  In both cases, the stream
    density is \(n = \SI{1}{cm^{-3}}\) and the central star is a
    \SI{10}{M_\odot} main-sequence B star (see Tab.~\ref{tab:stars}).
    Upper panels show the evolution of the grain position, \(R\) (blue
    curve, normalized by the rip point radius, \(R_\dag\)), and grain
    velocity, \(v\) (orange curve, normalized by the gas stream
    velocity).  The origin of the time axis is set to the moment of
    closest approach of the grain to the star: \(R = \Rmin\).  Lower
    panels show the trajectories in phase space: position versus
    gas--grain relative slip velocity (\(w = \abs{v - v_\infty}\)).  Filled
    contours show the net force on the grain: \(f\rad - f\drag\), with
    positive values in blue and negative values in red.  The heavy
    dotted line shows where there is no net force: \(f\rad = f\drag\).
    The grain trajectory (thick, solid black line with arrows)
    initially follows this line, but departs from it after the rip
    point. In the left panel, the grain enters a limit cycle between
    decoupling (rip) and re-coupling (snap back).  In the right panel,
    the grain spirals in on the stagnant drift point.  See text for
    further details.}
    \label{fig:phase-space-trajectories}
\end{figure*}

@@

An example of each of these two behaviors is illustrated in
Figure~\ref{fig:phase-space-trajectories}.  The left panels show the
case where \(v_\infty = \SI{40}{km.s^{-1}}\), which is in the unstable
regime, resulting in periodic ``limit-cycle'' behavior (the parameters
of this model correspond to the yellow ``plus'' symbol labeled ``40''
in the left panel of Fig.~\ref{fig:existence-dust-wave}).  During the
grain's first approach, it starts to follow a phase trajectory (lower
left panel) along the \(f\rad - f\drag = 0\) contour, corresponding to
equilibrium drift, in which the grain begins to move a few
\si{km.s^{-1}} slower than the gas stream.  Then, when it reaches the
rip point (\(R = R_\dag\), \(w \approx \SI{10}{km.s^{-1}}\)) it suddenly
experiences a large unbalanced outward radiation force (blue region of
phase space in Fig.~\ref{fig:phase-space-trajectories}). The grain's
inward momentum carries it to the point \(\Rmin \approx 0.85 R_\dag\), before
it is expelled at roughly twice the inflow speed.  However, after
moving outward, it finds itself in a drag-dominated region of phase
space (red in the figure), and so recouples to the inflowing gas
stream.  The recoupling initiates gradually, as the grain's outward
motion is slowed and turns around, but is completed suddenly once
\(w\) again falls below \SI{10}{km.s^{-1}}, in what we term
\textit{snap back}. The net result is that the grain has returned to
exactly the same phase track that it started in on, and so repeats the
cycle indefinitely.

@@

If \(r\B / \Rmin \ll 1\), then the grains are so strongly coupled to the
field that they can be treated in the guiding-center approximation, in
which the trajectory is decomposed into a tight circular gyromotion
around the field lines, plus a sliding of the guiding center along the
field lines, which is governed by the radiation and drag forces.  The
radiation force will also produce an out-of-plane drift, given by
\begin{equation}
  \label{eq:perpendicular-drift}
  \bm{v}_{\text{drift}} = \frac{c}{e z\grain} \, \frac{\bm{f}\!\rad \times \bm{B}}{B^2}
  \ ,
\end{equation}
but from equations~(\ref{eq:Larmor}, \ref{eq:dust-rad-force},
\ref{eq:dust-r0}) it follows that
\begin{equation}
  \label{eq:vdrift-over-vinfinity}
  \frac{v_{\text{drift}}(R\starstar)}{v_\infty} = \frac{r\B}{2 R\starstar} \ ,
\end{equation}
so it is valid to ignore this drift in the limit of small \(r\B\).
This is the limit that was applied in \S~\ref{sec:tight-magn-coupl}
for the case of zero drag.  In the opposite limit,
\(r\B / \Rmin \gg 1\), magnetic coupling is so weak that the
non-magnetic results of \S~\ref{sec:imperf-coupl-betw} are scarcely
modified.  Assuming \(w_\perp \sim v_\infty\) and adopting a threshold of
\(r\B / \Rmin < 0.1\), equations~(\ref{eq:larmor-over-Rdag},
\ref{eq:larmor-over-Rstarstar}) can be transformed into conditions on
the stream velocity (in \si{km.s^{-1}}) where tight magnetic coupling
will apply: \(v_{\infty} < v\freeze\), where
\begin{equation}
  \label{eq:velocity-strong-B-coupling}
  \begin{aligned}
    \text{drag-confined:}\quad v\freeze
    &\approx 0.8 \, a_{\si{\um}}^{-2} \, v\alfven \, L_4^{1/2} \ , \\
    \text{inertia-confined:}\quad v\freeze
    &\approx 6 \, a_{\si{\um}}^{-1} \, v\alfven^{1/3} \, n^{1/6} \, L_4^{1/3} \ ,
  \end{aligned}
\end{equation}
in which we have substituted typical values of the minor parameters
\(\Xi_\dag\), \(\phi_{\dag}\), \(\phi_{**}\), \(\rho\grain\),
\(T_4\).\footnote{%
  The most significant systematic variation in \(v\freeze\) from these
  suppressed parameters is due to grain composition, yielding slightly
  higher values for graphite than for silicate (\SI{+-0.15}{dex}).} %
It is apparent that \(v\freeze\) is very sensitive to the grain size.
For instance, taking a typical \hii{} region value of
\(v\alfven = \SI{2}{km.s^{-1}}\) \citep{Arthur:2011a} and
\(L_4 = 0.63\) (Tab.~\ref{tab:stars}, B1.5~V star), then for the
drag-confined case \(v\freeze \approx \SI{30}{km.s^{-1}}\) for \SI{0.2}{\um}
grains but \(v\freeze \approx \SI{3000}{km.s^{-1}}\) for \SI{0.02}{\um}
grains. Thus, for typical stream velocities of
\SIrange{20}{100}{km.s^{-1}}, the small grains are always tightly
coupled to the magnetic field, but the large grains are only loosely
coupled for the faster streams.

@@

In panel~b, corresponding to \(v_\infty = \SI{80}{km.s^{-1}}\), the grain
settles for a while around the stagnant drift radius, \(R_\ddag\), after
the initial rip and turn around.  Again, it slowly migrates sideways,
and eventually recouples to the incident stream, but this time after
reaching \(y \approx +R_\ddag\).  The grain residence time in the apex region,
measured in crossing times, is slightly longer than in panel~a, but is
of the same order.  In both these cases a second, exterior dust
shell is formed in addition to the hemispherical one produced by the
initial turn around inside \(R_\dag\). In the limit-cycle case, it forms
at the snap-back point, while in the stagnant-drift case, it forms at
\(R_\ddag\) and is significantly denser than the interior shell (upper
right panel of Fig.~\ref{fig:frozen-stream}).
